### 2018-05-11 manuscript/data.tex
data updated

Over the releasing time period from June to October in 2015, 25481 individules (XX\% females and XX\% males)were reached and XXX trips are collected, XX trips per individual. Figure~\ref{fig:data_over} lists the XX variables, falling into 8 domains. Those domains give a generalized depiction of the individual characteristics and serve as the ingredients for the analysis of urban dynamics over diverse people.

Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, a series of preliminary statistics is performed to check whether it is rich enough to represent a wide range of human individuals in the city.

@@

In the report (looking for some report), the penetration of mobile device is XXX, almost every XX people got a Mobile Phone in the urban. Figure~\ref{fig:data_age_edu} shows samples covering a wide range of all ages, dominately between 18 to 45. According to the 2015 Annual Census Statistics report~\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. The distribution aligns to the fact that Shenzhen is a city where the majority is young people. The education levels is diverse from low to high.

@@

Figure~\ref{fig:data_geometry} shows the statistics of spatial activity. The activity time distribution in traveling obeys the commen sense. Morning and late afternoon peaks are detected in the data. The house distribution reports that our data has higher dense sampling in Futian, Nanshan districts, because those two are the most developed districts in Shenzhen.

@@

>>>>

Over the releasing time period from June to October in 2015, 25481 individules (48\% females and 52\% males) were reached and XXX trips are collected. The majority of our 25481 volunteers contribute XXX trips. Figure~\ref{fig:data_over} lists the XX variables, falling into 8 domains. Those domains give a generalized depiction of the individual characteristics and serve as the ingredients for the analysis of urban dynamics over diverse people.

Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of individuals in the city.

@@

In the report (looking for some report), the penetration of mobile device is XXX, almost every XX people got a Mobile Phone in the urban. Figure~\ref{fig:data_age_edu} shows samples covering a wide range of all ages, dominately between 18 to 45. There is also a few records pertaining to individuals below the age of 18 or above 70. The distribution aligns to the fact that Shenzhen is a city where the majority is young people. According to the 2015 Annual Census Statistics report~\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. Figure~\ref{fig:data_age_edu} gives the distribution of education levels, diverse from low to high.

@@

Figure~\ref{fig:data_geometry} shows the statistics of spatial related activity. In Figure~\ref{fig:data_geometry}(a), ...The activity time distribution in traveling obeys the commen sense. Morning and late afternoon peaks are detected in the data. Figure~\ref{fig:data_geometry}(b) shows the map of the origins and destinations spot by volunteers in Shenzhen. It shows that more trips uploaded by volunteers located in Futian and Nanshan districts, the city's heart part of than the surrounding outer areas. This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.

Trips are uploaded in a wide range of purpose in addition to home, work, but also includes XX entertainment, visiting, etc. The diverse purposes make it possible to characterize the flows across the city between different functional places.

@@

While the subset can not fully represent the ground true of society awide, the distribution shows positive sign in even indication. We takes it as a step into the social-spatial dynamics exploration in the context of big social media data. 
% As a note, although it is a subset of all people with
